Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-19 manuscript.Rmd
Fixed first small multiples plot after finding bug. Reformatting needed and updates to large small multiples necessary.

 abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
 abb$ID <- 1:nrow(abb)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

@@

 plotSmallMultiples.a <-  ggplot(reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ],  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ], 
               aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
      geom_text(data = reduced.ldata, aes(x =xpos, y = ypos, label = lab), size = 5) +
     theme_bw() +
     theme(strip.text.x = element_text(size = 12)) + 
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size = 10)) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = "#e66101") + 
     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = "#533c99") 
     #ggtitle("Figure 1. Comparison of Historical Database with Scopus\n for Journals with Highest Output (1989 - 2013)") + 
     # theme(plot.title = element_text(size = 19))
     # 
#ggsave(file = "scopusComparison.png", plotSmallMultiples.a)

>>>>

# Read Scopus data
scopus.df$Year <- as.numeric(scopus.df$Year)
scopus.df <- filter(scopus.df, Year <= 2013)

# Join with historical database
sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
    select(Year, Journal, N, Overall.N, Documents)

sm.scopus.merged-counts <- group_by(sm.scopus.merged, Journal) %>%
     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
     arrange(desc(DataBase.N))

 abb$ID <- 1:nrow(abb)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

@@

new.data <- reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ]
new.data

 plotSmallMultiples.a <-  ggplot(new.data,  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Journal %in% titles.reduced.a, ], 
               aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
    geom_text(data = reduced.ldata, aes(x =xpos, y = ypos, label = lab), size = 5) +
     theme_bw() +
     theme(strip.text.x = element_text(size = 12)) + 
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size = 10)) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = "#e66101") + 
     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = "#533c99") 
     #ggtitle("Figure 1. Comparison of Historical Database with Scopus\n for Journals with Highest Output (1989 - 2013)") + 
     # theme(plot.title = element_text(size = 19))
     # 
#ggsave(file = "scopusComparison.png", plotSmallMultiples.a)
